%!TEX root = constitution.tex
\section{Benefits and Payments to Charity Trustees and Connected Persons}\label{sec:benefits}
    \subsection{General Provisions}
    No charity trustee or connected person may:
    \begin{enumerate}
        \item buy or receive any goods or services from \shortname{} on terms preferential to those applicable to members of the public;
        \item sell goods, services, or any interest in land to \shortname{};
        \item be employed by, or receive any remuneration from, \shortname{};
        \item receive any other financial benefit from \shortname{};
    \end{enumerate}
    unless the payment or benefit is permitted by clause~\ref{sec:permitted_benefits}, or authorised by the court or the prior written consent of the Charity Commission (`the Commission') has been obtained. In this clause, a `financial benefit' means a benefit, direct or indirect, which is either money or has a monetary value.

    \subsection{Scope and Powers Permitting Trustees' or Connected Persons' Benefits}\label{sec:permitted_benefits}
    \begin{enumerate}
        \item A charity trustee or connected person may receive a benefit from \shortname{} as a beneficiary of \shortname{} provided that a majority of the trustees do not benefit in this way.
        \item A charity trustee or connected person may enter into a contract for the supply of services, or of goods that are supplied in connection with the provision of services, to \shortname{} where that is permitted in accordance with, and subject to the conditions in, section 185 to 188 of the Charities Act 2011.
        \item\label{item:goods} Subject to clause~\ref{sec:goods_controls} a charity trustee or connected person may provide \shortname{} with goods that are not supplied in connection with services provided to \shortname{} by the charity trustee or connected person.

        \item A charity trustee or connected person may receive interest on money lent to \shortname{} at a reasonable and proper rate which must be not more than the Bank of England bank rate (also known as the base rate).
        \item A charity trustee or connected person may receive rent for premises let by the trustee or connected person to \shortname{}. The amount of the rent and the other terms of the lease must be reasonable and proper. The charity trustee concerned must withdraw from any meeting at which such a proposal or the rent or other terms of the lease are under discussion.
        \item A charity trustee or connected person may take part in the normal trading and fundraising activities of \shortname{} on the same terms as members of the public.
    \end{enumerate}

    \subsection{Payment for Supply of Goods Only --- Controls}\label{sec:goods_controls}
    \shortname{} and its charity trustees may only rely upon the authority provided by item~\ref{item:goods} of clause~\ref{sec:permitted_benefits} if each of the following conditions is satisfied:
    \begin{enumerate}
        \item The amount or maximum amount of the payment for the goods is set out in a written agreement between \shortname{} and the charity trustee or connected person supplying the goods (`the supplier').
        \item The amount or maximum amount of the payment for the goods does not exceed what is reasonable in the circumstances for the supply of the goods in question.
        \item The other charity trustees are satisfied that it is in the best interests of \shortname{} to contract with the supplier rather than with someone who is not a charity trustee or connected person. In reaching that decision the charity trustees must balance the advantage of contracting with a charity trustee or connected person against the disadvantages of doing so.
        \item The supplier is absent from the part of any meeting at which there is discussion of the proposal to enter into a contract or arrangement with them with regard to the supply of goods to \shortname{}.
        \item The supplier does not vote on any such matter and is not to be counted when calculating whether a quorum of charity trustees is present at the meeting.
        \item The reason for their decision is recorded by the charity trustees in the minute book.
        \item A majority of the charity trustees then in office are not in receipt of remuneration or payments authorised by clause~\ref{sec:benefits}.
    \end{enumerate}
