%!TEX root = constitution.tex
\section{Charity Trustees}
\label{sec:trustees}

    \subsection{Functions and Duties of Charity Trustees}\label{sec:trustee_duties}
    The charity trustees shall manage the affairs of \shortname{} and may for that purpose exercise all the powers of \shortname{}. It is the duty of each charity trustee:

        \subsubsection{}
        to exercise his or her powers and to perform his or her functions as a trustee of \shortname{} in the way he or she decides in good faith would be most likely to further the purposes of \shortname{}; and

        \subsubsection{}
        to exercise, in the performance of those functions, such care and skill as is reasonable in the circumstances having regard in particular to:
        \begin{enumerate}
            \item any special knowledge or experience that he or she has or holds himself or herself out as having; and
            \item if he or she acts as a charity trustee of \shortname{} in the course of a business or profession, to any special knowledge or experience that it is reasonable to expect of a person acting in the course of that kind of business or profession.
        \end{enumerate}

    \subsection{Eligibility for Trusteeship}\label{sec:trustee_eligibility}

        \subsubsection{}
        Every charity trustee must be a natural person.

        \subsubsection{}
        No one may be appointed as a charity trustee:
        \begin{enumerate}
            \item if he or she is under the age of 16 years; or
            \item if he or she would automatically cease to hold office under the provisions of item~\ref{item:trustee_disqualification} of clause~\ref{sec:retirement}.
        \end{enumerate}

        \subsubsection{}
        No one is entitled to act as a charity trustee whether on appointment or on any re-appointment until he or she has expressly acknowledged, in whatever way the charity trustees decide, his or her acceptance of the office of charity trustee.

        \subsubsection{}
        At least one of the trustees of \shortname{} must be 18 years of age or over. If there is no trustee aged at least 18 years, the remaining trustee or trustees may act only to call a meeting of the charity trustees, or appoint a new charity trustee.

    \subsection{Number of Charity Trustees}\label{sec:trustee_numbers}

        \subsection{}\label{sec:min_max}
        There should be:
        \begin{enumerate}
            \item No fewer than 3 and no more than 6 elected trustees
            \item One ex officio trustee
        \end{enumerate}

        \subsection{}
        There must be at least three charity trustees. If the number falls below this minimum, the remaining trustee or trustees may act only to call a meeting of the charity trustees, or appoint a new charity trustee.

        \subsection{}
        The maximum number of charity trustees that can be appointed is as provided in clause~\ref{sec:min_max}. No trustee appointment may be made in excess of these provisions.

        \subsection{First Charity Trustees}\label{sec:first_trustees}
        The first charity trustees of \shortname{} are:
        \begin{itemize}
            \item Mr Peter Inglesby
            \item Mr Kristian Glass
            \item Mr Zeth Green
            \item Mr Owen Campbell
        \end{itemize}
