%!TEX root = constitution.tex
\section{Meetings and Proceedings of Charity Trustees}\label{sec:meetings}

    \subsection{Calling Meetings}
    Any charity trustee may call a meeting of the charity trustees.

    Subject to that, the charity trustees shall decide how their meetings are to be called, and what notice is required.

    \subsection{Chairing of Meetings}\label{sec:chairing_of_meetings}
    The charity trustees may appoint one of their number to chair their meetings and may at any time revoke such appointment. If no-one has been so appointed, or if the person appointed is unwilling to preside or is not present within 10 minutes after the time of the meeting, the charity trustees present may appoint one of their number to chair that meeting.

    \subsection{Procedure at Meetings}

        \subsubsection{}
        No decision shall be taken at a meeting unless a quorum is present at the time when the decision is taken. The quorum is two charity trustees, or the number nearest to one third of the total number of charity trustees, whichever is greater, or such larger number as the charity trustees may decide from time to time. A charity trustee shall not be counted in the quorum present when any decision is made about a matter upon which he or she is not entitled to vote.

        \subsubsection{}
        Questions arising at a meeting shall be decided by a majority of those eligible to vote.

        \subsubsection{}
        In the case of an equality of votes, the chair shall have a second or casting vote.

    \subsection{Participation in Meetings by Electronic Means}

        \subsubsection{}
        A meeting may be held by suitable electronic means agreed by the charity trustees in which each participant may communicate with all the other participants.

        \subsubsection{}
        Any charity trustee participating at a meeting by suitable electronic means agreed by the charity trustees in which a participant or participants may communicate with all the other participants shall qualify as being present at the meeting.

        \subsubsection{}
        Meetings held by electronic means must comply with rules for meetings, including chairing and the taking of minutes.
